% -------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
% ------------------------

% ------------------------
% Original Overleaf template: https://www.overleaf.com/latex/templates/jakes-resume-anonymous/cstpnrbkhndn
% ------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}


% ----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}
% \usepackage{times}
% \usepackage{helvet}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generated PDF is machine readable/ATS parsable.
\pdfgentounicode=1

% -------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{-2pt}\textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


% ----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\huge \scshape Harsh Kapadia} \\ \vspace{5pt}
    \small
    \href{https://harshkapadia.me}{harshkapadia.me} $|$ \href{https://github.com/HarshKapadia2}{github.com/HarshKapadia2} $|$ \href{https://linkedin.com/in/harshgkapadia}{linkedin.com/in/harshgkapadia} $|$ \href{mailto:contact@harshkapadia.me}{contact@harshkapadia.me}
    \vspace{-8pt}
\end{center}


% -----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Boston University -- The Graduate School of Arts \& Sciences (GRS)}{Dec 2023}
            {Master of Science in Computer Science (CGPA: 3.0 / 4.0)}{Boston, USA}
            \resumeItemListStart
                \resumeItem{Courses: Computer Networks, Transport Protocol `\href{https://networking.harshkapadia.me/files/homa/report}{Homa}', Network Security, Operating Systems, Databases}
            \resumeItemListEnd

        \resumeSubheading
            {University of Mumbai -- Thadomal Shahani Engineering College}{May 2022}
            {Bachelor of Engineering in Information Technology (CGPA: 9.02 / 10.0)}{Mumbai, India}
            \resumeItemListStart
                \resumeItem{Courses: Web Dev., Computer Networks, Network Security, Database Management, Project Management}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-18pt}


% -----------EXPERIENCE-----------
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Advanced Micro Devices (AMD), Inc.}{Jan 2024 -- present}
            {Field Applications Engineer}{Austin, USA}
    \resumeSubHeadingListEnd
% \vspace{-15pt}
\vspace{-12pt}


% -----------INTERNSHIPS-----------
\section{Internships}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Advanced Micro Devices (AMD), Inc.}{May 2023 -- Aug 2023}
            {Field Applications Engineering Intern}{Austin, USA}
            \resumeItemListStart
                \resumeItem{Built a web app to provision and manage Virtual Machines configured with debug software and scripts, user public keys, persistent storage and VNC to reduce server issue debug time by 10\%, using KVM, Bash scripts, Express.js and React.js.}
                \resumeItem{Benchmarked network bandwidth (iperf3), memory bandwidth (STREAM) and CPU performance (DGEMM) of servers.}
            \resumeItemListEnd

        \resumeSubheading
            {NanoNet Technologies Inc.}{Aug 2021 -- Nov 2021}
            {Software Intern}{Remote}
            \resumeItemListStart
                \resumeItem{Published two \href{https://www.npmjs.com/package/@nanonets/optical-character-recognition}{OCR} and \href{https://www.npmjs.com/package/@nanonets/image-classification}{Image Classification} SDKs to improve development time by 50\%.}
                \resumeItem{Enhanced documentation by enforcing the OpenAPI 3.1.0 standard and adding more code samples.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


% -----------SKILLS-----------
\section{Skills}
    \vspace{-2pt}
    \begin{itemize}[leftmargin=0.2in, label={}]
        {\item{
            \begin{tabular}{ l@{\hskip 0.2in} l }
                 \textbf{Web}: React.js, Express.js, Flask, HTML, CSS, JS & \textbf{Languages}: JavaScript, Java, Bash, Python, C \\ 
                 \textbf{Databases}: MySQL, MongoDB & \textbf{Platforms}: GitHub, Firebase, Heroku \\  
                 \textbf{Tools}: Git, iperf3, Wireshark, Tcpdump & \textbf{CI/CD}: GitHub Actions
            \end{tabular}
        }}
    \end{itemize}
\vspace{-20pt}


% -----------PROJECTS-----------
\section{Projects}
    \vspace{-6pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\normalsize{Git Graph}} $|$ \emph{React.js} $|$ \href{https://git-graph.harshkapadia.me}{Web app}, \href{https://github.com/HarshKapadia2/git-graph}{GitHub}}{Jan 2022 -- Jul 2022}
            \resumeItemListStart
                \resumeItem{A web app to visualize the graphs that Git creates to connect Commit, Tree and Blob objects internally.}
                \resumeItem{Takes an existing repository to generate graph visualizations for local branches and allows highlighting specific commits.}
                \resumeItem{Taught 100+ people the internals of Git using Git Graph in \href{https://talks.harshkapadia.me/git_internals}{my talks}.}
            \resumeItemListEnd
        \vspace{-15pt}

        \resumeProjectHeading
            {\textbf{\normalsize{Performance Comparison of TCP Versions}} $|$ \emph{iperf3, GENI Testbed} $|$ \href{https://harshkapadia2.github.io/tcp-version-performance-comparison}{Report}, \href{https://github.com/HarshKapadia2/tcp-version-performance-comparison}{GitHub}}{Nov 2022 -- Dec 2022}
            \resumeItemListStart
                \resumeItem{Compared Congestion Window size responses of TCP Reno, TCP CUBIC, TCP Vegas and TCP BBR to network congestion.}
                \resumeItem{Compared the fairness of two TCP versions running simultaneously on the same connection.}
            \resumeItemListEnd
        \vspace{-15pt}

        \resumeProjectHeading
            {\textbf{\normalsize{Git Internals}} $|$ \emph{Asciidoctor Jet} $|$ \href{https://git.harshkapadia.me}{PWA}, \href{https://github.com/HarshKapadia2/git_internals}{GitHub}}{May 2022 -- Jul 2022}
            \resumeItemListStart
                \resumeItem{A PWA documenting and explaining the internals of Git.}
                \resumeItem{Explains the contents of the \texttt{.git} directory and the connections between Commit, Tree and Blob objects.}
            \resumeItemListEnd
        \vspace{-15pt}

        \resumeProjectHeading
            {\textbf{\normalsize{HPS Gems}} $|$ \emph{PHP, MySQL, HTML, CSS, JS, Heroku} $|$ \href{https://hps-gems.herokuapp.com}{Web app}, \href{https://github.com/HarshKapadia2/hps-gems}{GitHub}}{Oct 2020 -- Dec 2020}
            \resumeItemListStart
                \resumeItem{A JAMstack e-Commerce CRUD web app for selling raw gemstones.}
                \resumeItem{Uses the Fetch API to interface with the backend and the Web Components API to render products.}
            \resumeItemListEnd
        \vspace{-15pt}

        \resumeProjectHeading
            {\textbf{\normalsize{OTC CatchUp}} $|$ \emph{Express.js, Asciidoctor Jet, Bash, HTML, CSS, JS, Deta} $|$ \href{https://catchup.ourtech.community}{Web app}, \href{https://github.com/OurTechCommunity/catchup}{GitHub}}{Sep 2021 -- present}
            \resumeItemListStart
                \resumeItem{A web app for managing weekly OTC CatchUp Tech discussion sessions.}
                \resumeItem{Hosts session summaries and manages session joining links.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}


% -----------EXTRACURRICULAR ACTIVITY-----------
\section{Extracurricular Activity}
    \resumeSubHeadingListStart
        \resumeSubheading
            {\textbf{\normalsize{Our Tech Community (OTC)}} $|$ {\normalfont \href{https://ourtech.community}{ourtech.community}}}{Jan 2020 -- present}
            {Organiser}{}
            \resumeItemListStart
                \resumeItem{Started a Tech-loving open-to-all community with 500+ current members.}
                \resumeItem{Hosted 800+ hours of weekly \href{https://catchup.ourtech.community}{OTC CatchUp} sessions involving technical discussions, project showcases and talks.}
            \resumeItemListEnd

        \resumeSubheading
            {\textbf{\normalsize{Talks}} $|$ {\normalfont \href{https://talks.harshkapadia.me}{talks.harshkapadia.me}}}{Jun 2020 -- present}
            {}{}
            \vspace{-15pt}
            \resumeItemListStart
                \resumeItem{Impacted 700+ people in 20+ talks and workshops at various technical meetups.}
                \resumeItem{Gave talks on `\href{https://talks.harshkapadia.me/mac-and-ip-routing/content}{Routing Using IP and MAC Addresses}', \href{https://talks.harshkapadia.me/git_internals}{Git internals}, etc.}
            \resumeItemListEnd

        \resumeSubheading
            {\textbf{\normalsize{Articles}} $|$ {\normalfont \href{https://networking.harshkapadia.me}{networking.harshkapadia.me}}}{Dec 2020 -- present}
            {}{}
            \vspace{-15pt}
            \resumeItemListStart
                \resumeItem{Wrote detailed articles on \href{https://networking.harshkapadia.me/tls}{TLS}, \href{https://networking.harshkapadia.me/ssh}{SSH}, \href{https://talks.harshkapadia.me/mac-and-ip-routing/content}{IP and MAC Routing}, \href{https://networking.harshkapadia.me/homa}{Homa}, etc. by analysing packet captures.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
