% -------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
% ------------------------

% ------------------------
% Original Overleaf template: https://www.overleaf.com/latex/templates/jakes-resume-anonymous/cstpnrbkhndn
% ------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}


% ----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}
% \usepackage{times}
% \usepackage{helvet}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generated PDF is machine readable/ATS parsable.
\pdfgentounicode=1

% -------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{-2pt}\textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


% ----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\huge \scshape Harsh Kapadia} \\ \vspace{1pt}
    \small
    \faGlobe \href{https://harshkapadia.me}{\raisebox{-0.1\height}\ harshkapadia.me} ~
    \faGithub \href{https://github.com/HarshKapadia2}{\raisebox{-0.2\height}\ github.com/HarshKapadia2} ~
    \faLinkedin \href{https://linkedin.com/in/harshgkapadia}{\raisebox{-0.2\height}\ linkedin.com/in/harshgkapadia} ~
    \faEnvelope \href{mailto:contact@harshkapadia.me}{\raisebox{-0.2\height}\  contact@harshkapadia.me}
    \vspace{-13pt}
\end{center}


% -----------EDUCATION-----------
\section{Education}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Boston University -- The Graduate School of Arts \& Sciences (BU GRS)}{Dec 2023 (exp)}
            {Master of Science in Computer Science (SGPI: 3.80 / 4.0)}{Boston, USA}
            \resumeItemListStart
                \resumeItem{Coursework: Grad. Intro. to Computer Networks, Grad. Intro. to Databases, Object Oriented Software Design}
            \resumeItemListEnd
        \vspace{-3pt}

        \resumeSubheading
            {University of Mumbai -- Thadomal Shahani Engineering College}{May 2022}
            {Bachelor of Engineering in Information Technology (CGPA: 9.02 / 10.0)}{Mumbai, India}
            \resumeItemListStart
                \resumeItem{Selected coursework: Web Dev., Computer Networks, Network Security, Enterprise Network Design, DBMS, Adv. Data Management, Cloud Computing, Operating Systems, Data Structures, Analysis of Algorithms, Project Management}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-19pt}


% -----------SKILLS-----------
\section{Skills}
    \vspace{-4pt}
    \begin{itemize}[leftmargin=0.2in, label={}]
        {\item{
            \begin{tabular}{ l@{\hskip 0.2in} l }
                 \textbf{Web}: React.js, Node.js (Express.js), Flask, HTML, CSS, JS & \textbf{Languages}: JavaScript, Java, Python, C \\ 
                 \textbf{Databases}: MySQL, MongoDB & \textbf{Platforms}: GitHub, Firebase, Heroku, Deta \\  
                 \textbf{Tools}: \href{https://git.harshkapadia.me}{Git}, \href{https://networking.harshkapadia.me}{Wireshark}, \href{https://harshkapadia2.github.io/asciidoctor-jet}{Asciidoctor Jet}, Figma & \textbf{CI/CD}: GitHub Actions
            \end{tabular}
        }}
    \end{itemize}
\vspace{-22pt}


% -----------EXPERIENCE-----------
\section{Experience}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {NanoNet Technologies Inc.}{Aug 2021 -- Nov 2021}
            {Software Intern}{}
            \resumeItemListStart
                \resumeItem{Published two Node.js SDKs on npm for their \href{https://www.npmjs.com/package/@nanonets/optical-character-recognition}{OCR} and \href{https://www.npmjs.com/package/@nanonets/image-classification}{Image Classification} REST APIs.}
                \resumeItem{Migrated their API specification from Swagger 2.0 to OpenAPI 3.1.0.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-20pt}


% -----------PROJECTS-----------
\section{Projects}
    \vspace{-8.5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\normalsize{Git Graph}} $|$ \emph{React.js, GitHub Pages} $|$ \href{https://git-graph.harshkapadia.me}{Web app}, \href{https://github.com/HarshKapadia2/git-graph}{GitHub}}{Jan 2022 -- present}
            \resumeItemListStart
                \resumeItem{A web app to visualize the graphs that Git creates to connect Commit, Tree and Blob objects internally.}
                \resumeItem{Takes an existing repository to generate graph visualizations for local branches and allows highlighting specific commits.}
            \resumeItemListEnd
        \vspace{-19pt}

        \resumeProjectHeading
            {\textbf{\normalsize{Performance Comparison of TCP Versions}} $|$ \emph{GENI, Shell, R} $|$ \href{https://harshkapadia2.github.io/tcp-version-performance-comparison}{Report}, \href{https://github.com/HarshKapadia2/tcp-version-performance-comparison}{GitHub}}{Nov 2022 -- Dec 2022}
            \resumeItemListStart
                \resumeItem{Compared Congestion Window size responses of TCP Reno, TCP CUBIC, TCP Vegas and TCP BBR to network congestion.}
                \resumeItem{Compared the fairness of two TCP versions running simultaneously on the same connection.}
            \resumeItemListEnd
        \vspace{-19pt}

        \resumeProjectHeading
            {\textbf{\normalsize{Git Internals}} $|$ \emph{Asciidoctor Jet, GitHub Pages} $|$ \href{https://git.harshkapadia.me}{PWA}, \href{https://github.com/HarshKapadia2/git_internals}{GitHub}}{May 2020 -- present}
            \resumeItemListStart
                \resumeItem{A PWA documenting and explaining the internals of Git.}
                \resumeItem{Explains the contents of the \texttt{.git} directory and the connections between Commit, Tree and Blob objects.}
            \resumeItemListEnd
        \vspace{-19pt}

        \resumeProjectHeading
            {\textbf{\normalsize{HPS Gems}} $|$ \emph{PHP, MySQL, HTML, CSS, JS, Heroku} $|$ \href{https://hps-gems.herokuapp.com}{Web app}, \href{https://github.com/HarshKapadia2/hps-gems}{GitHub}}{Oct 2020 -- Dec 2020}
            \resumeItemListStart
                \resumeItem{A JAMstack e-Commerce CRUD web app for selling raw gemstones.}
                \resumeItem{Users can add items to their cart, place orders and view their shopping history and profile.}
                \resumeItem{Uses the Fetch API to connect with the PHP API and uses the Web Components API to optimize rendering products.}
            \resumeItemListEnd
        \vspace{-19pt}

        \resumeProjectHeading
            {\textbf{\normalsize{OTC CatchUp}} $|$ \emph{Express.js, Asciidoctor Jet, Shell, HTML, CSS, JS, Deta} $|$ \href{https://catchup.ourtech.community}{Web app}, \href{https://github.com/OurTechCommunity/catchup}{GitHub}}{Sep 2021 -- present}
            \resumeItemListStart
                \resumeItem{Created a web app for managing weekly OTC CatchUp Tech discussion sessions.}
                \resumeItem{Hosts session summaries created using Asciidoctor Jet and manages session joining links using Deta Base.}
                \resumeItem{Currently helping manage active Open Source contributions to the project.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-19pt}


% -----------COMMUNITY ACTIVITY-----------
\section{Community Activity}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {\textbf{\normalsize{Our Tech Community (OTC)}} $|$ {\normalfont \href{https://ourtech.community}{ourtech.community}}}{Jan 2020 -- present}
            {Organiser}{}
            \vspace{-7pt}
            \resumeItemListStart
                \resumeItem{Started a Tech-loving open-to-all community with 450+ current members.}
                \resumeItem{Hosted 600+ hours of weekly \href{https://catchup.ourtech.community}{OTC CatchUp} sessions involving technical discussions, project showcases and talks.}
                \resumeItem{Organised an in-person \href{https://meetup.ourtech.community}{OTC MeetUp} event with 60+ attendees.}
            \resumeItemListEnd
        \vspace{-4pt}

        \resumeSubheading
            {\textbf{\normalsize{Talks}} $|$ {\normalfont \href{https://talks.harshkapadia.me}{talks.harshkapadia.me}}}{Jun 2020 -- present}
            {}{}
            \vspace{-18pt}
            \resumeItemListStart
                \resumeItem{Impacted 700+ people in 19+ talks and workshops at various technical meetups.}
                \resumeItem{Conducted in-person talks on \href{https://talks.harshkapadia.me/git_internals}{The Internals of Git} at TechTogether Boston 2022 and BostonHacks 2022.}
                \resumeItem{Gave talks on \href{https://gdsc.community.dev/events/details/developer-student-clubs-thadomal-shahani-engineering-college-mumbai-presents-git-and-github-workshop}{Git basics}, \href{https://gdsc.community.dev/events/details/developer-student-clubs-thadomal-shahani-engineering-college-mumbai-presents-git-internals-how-does-git-work}{Git internals} and \href{https://gdsc.community.dev/events/details/developer-student-clubs-thadomal-shahani-engineering-college-mumbai-presents-working-with-cicd-github-actions}{GitHub Actions} for GDSC TSEC with 200+ participants.}
            \resumeItemListEnd
        \vspace{-4pt}

        \resumeSubheading
            {\textbf{\normalsize{GitHub Campus Expert}}}{Oct 2021 -- present}
            {}{}
            \vspace{-18pt}
            \resumeItemListStart
                \resumeItem{One of the 82 students selected out of 8000+ applicants worldwide.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-19pt}


% -----------EXTRACURRICULAR ACTIVITY-----------
\section{Extracurricular Activity}
    \vspace{-2pt}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Hackathons}{Sep 2019 -- present}
            {}{}
            \vspace{-18pt}
            \resumeItemListStart
                \resumeItem{Organised three editions of TSEC CodeCell's TSEC Hacks (2020-22) with 200+ in-person participants.}
                \resumeItem{Mentored and judged in-person at HackMIT 2022, BostonHacks 2022 and TechTogether Boston 2022.}
            \resumeItemListEnd
        \vspace{-4pt}

        \resumeSubheading
            {Google Developer Student Clubs Boston University}{Sep 2022 -- present}
            {Tech Lead}{}
            \vspace{-7pt}
            \resumeItemListStart
                \resumeItem{Co-hosted a workshop on the basics of React.js.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-8pt}


\end{document}
